Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of NIRCam Detectors

### 2018-08-24 ms.tex
some more descriptions of tests.

\begin{deluxetable*}{ccCrlc}[b!]
\tablecaption{Summary of Ground-Based Tests}\label{tab:testSummary}
\tablecolumns{7}
%\tablenum{2}
\tablewidth{0pt}
\tablehead{
\colhead{Name} &
\colhead{Location} &
\colhead{UT dates} &
\colhead{Best Stability} & 
\colhead{Light Source} & 
\colhead{Instrument Mode} \\
\colhead{} &
\colhead{} &
\colhead{(YYYY-mm-dd)} &
\colhead{(ppm)} &
\colhead{}
}
\startdata
CV 3       & NASA Goddard  & 2016       & 500   & LED           & WLP8 imaging \\
OTIS       & NASA Goddard  & 2017       &       & Continuum     & Grism spectroscopy \\
GL dewar   & Steward Obs.  & 2015-2016  &       & LED	        & flood-illuminated imaging \\
Asic dewar & Steward Obs.  & 2017-2019  &       & LED           & pinhole flood-illuminated imaging \\
\enddata
\tablecomments{Cryogenic vacuum (CV).}
\end{deluxetable*}

>>>>

The instrument modes tested included mostly imaging with narrowband LEDs, but there was also a test with spectroscopy on a broadband source.
The WLP8 imaging tests are where a point source is de-focused by 8 waves with a weak lens (WLP8).
This mode was designed for wavefront sensing, but is also useful for high-precision time series because it spreads the light over many pixels.
The weak lens produces a point spread function (PSF) that is hexagonal like JWST's mirrors and has a flat-to-flat width of $\sim$108 pixels and a vertex-to-vertex width of $\sim$136 pixels.
The hexagonal PSF also has a central vertical peak which can be used for aperture centering.
The tests with dewars did not have NIRCam optics and instead were flood illuminated with a light source that had large spatial variations due to a non-uniform source.
One of the stability tests during the OTIS test at NASA Johnson was a grism spectroscopy mode that used the F322W2 to illuminate the detector with a slitless spectrum covering 2.4 to 4.0~$\mu$m.

\begin{deluxetable*}{ccCrlc}[b!]
\tablecaption{Summary of Ground-Based Tests}\label{tab:testSummary}
\tablecolumns{7}
%\tablenum{2}
\tablewidth{0pt}
\tablehead{
\colhead{Name} &
\colhead{Location} &
\colhead{UT dates} &
\colhead{Best Stability} & 
\colhead{Light Source} & 
\colhead{Instrument Mode} \\
\colhead{} &
\colhead{} &
\colhead{(YYYY-mm-dd)} &
\colhead{(ppm)} &
\colhead{}
}
\startdata
CV 3       & NASA Goddard  & 2016       & 500   	& LED           & WLP8 imaging \\
OTIS       & NASA Johnson  & 2017       &   2200    	& Continuum     & Grism spectroscopy \\
OTIS       & NASA Johnson  & 2017       &   21,000    	& Continuum     & WLP8 Imaging \\
GL dewar   & Steward Obs.  & 2015-2016  &       	& LED	        & flood-illuminated imaging \\
Asic dewar & Steward Obs.  & 2017-2019  &       	& LED           & pinhole flood-illuminated imaging \\
\enddata
\tablecomments{Cryogenic vacuum (CV).}
\end{deluxetable*}
